\LARGE \bf Informed sampling for kinodynamic planning by \\ Markov Chain Monte Carlo methods

### 2017-02-01 paper.tex
minor changes

\title{\LARGE \bf
Informed sampling by Markov Chain Monte Carlo methods
}

@@

Initially, 
when no path has yet to be found, 
the samples need to be drawn from the entire state space~$\calX$.
However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths}, which is the focus of this paper, can limit their sampling domain to a subset of~$\calX$  containing states that may produce higher-quality paths than~$\gamma$.
Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.

@@

Unfortunately, both rejection sampling and HRS may produce a large number of rejected samples especially in high-dimensional spaces.
This may cause the search algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
Our main insight is 
\os{this is a very important sentence!!!}
Specifically, our approach consists of two stages:
in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a gradient-descent algorithm;
in the second stage, this retracted sample $\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.

@@

\section{Motivating example---Minimal-Time Double Integrator}
We start by considering a simple yet important motion-planning problem---the double integrator.
We are given a one-dimensional point robot  with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
A state in this model is described by 
the position $q \in \R$
and
the velocity $\dot{q}\in \R$ of the position
%each coordinate axis.
The dynamics of the system is described by:
$$
x = (q, \dot{q}); 
\hspace{5mm}
u = \ddot{q}.
$$
Here, the control $u [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.

>>>>

\title{\LARGE \bf
Informed sampling for kinodynamic planning by \\ Markov Chain Monte Carlo methods
}

@@

Initially, 
when no path has yet to be found, 
the samples need to be drawn from the entire state space~$\calX$.
However, once a path $\gamma$ is produced,  algorithms that seek \emph{high-quality paths} can limit their sampling domain to a subset of~$\calX$ only  containing states that may produce higher-quality paths than~$\gamma$.
Following Gammell et al.~\cite{GSB14}, we call this subset the \emph{informed subset} and denote it~$\Cinf$.
\textbf{In this work we address the problem of efficiently producing samples in informed subset for systems with differential constraints}.

@@

Unfortunately, both rejection sampling and HRS may produce a large number of rejected samples especially in high-dimensional spaces.
This may cause the search algorithm to spend most of its time trying to produces samples in~$\Cinf$ rather than explore it.
In this paper, we suggest an alternative approach to produce samples in the informed set \Cinf for a wide range of settings.
\textbf{Our main insight is to formulate the problem as the problem of sampling uniformly below a level set of an implicit function and then apply optimization and statistical tools.}
Specifically, our approach consists of two stages:
in the first, a random sample $x \in \calX$ is retracted to the boundary of~$\Cinf$ by running a gradient-descent algorithm;
in the second stage, this retracted sample $\tilde{x}$ is used to seed a Monte Carlo sampling chain which allows us to  produce samples that (approximately) cover~$\Cinf$  uniformly.

@@

\section{Motivating example---Minimal-Time Double Integrator}
We start by considering a simple yet important motion-planning problem---the double integrator.
We are given a one-dimensional point robot  with bounded velocity and bounded acceleration moving amid obstacles. We wish to compute the minimal-time trajectory between two states $x_s, x_g$.
A state in this model is described by 
the position $q \in \R$
and
the velocity $\dot{q}\in \R$ of the position
%each coordinate axis.
The dynamics of the system is described by:
$$
x = (q, \dot{q}); 
\hspace{5mm}
u = \ddot{q}.
$$
Here, the control $u \in [u_{\text{min}}, u_{\text{max}}]$ is the (bounded) acceleration.
